Kindly Bent to Free Us

### 2019-07-10 kindly/infer/extra.tex
Add the proof for completeness.

\section{Inference rules}
\label{appendix:infer}

\begin{figure*}[htp]
  \input{infer/typing}
  \caption{Type inference algorithm -- $\inferW{\Sigma}{(C,\psi)}{\bf{\E}}{\bf{e}}{\tau}$ }
  \label{rules:typing}
\end{figure*}

\begin{figure}[tp]
  \centering
  \begin{mathpar}
    { \Weaken_{\bvar{x}{\sigma}}(\Sv) =
      \begin{dcases}
        \Ctrue& \text{if } x\in\Sv\\
        \Cleq{\sigma}{\kaff_\infty}&\\
      \end{dcases}
    }

    \inferrule{
      \inferK{C \Cand C_x} \E \tau {k'} \\
      D = C \Cand C_x \Cand \Cleq{k'}k
    }{
      \E \vdash \Cleq{\forall \kvar_i \forall (\tvar_j:k_j).\ \qual{C_x}{\tau}}{k} \Crewrite  D
    }
  \end{mathpar}
  \caption{Auxiliary rules for inference}
  \label{op:usgmap}
\end{figure}

>>>>

\section{Type Inference}
\label{appendix:infer}

\begin{figure*}[p]
  \input{infer/typing}
  \caption{Type inference rules -- $\inferW{\Sigma}{(C,\psi)}{\bf{\E}}{\bf{e}}{\tau}$ }
  \label{rules:typing:full}
\end{figure*}

In this appendix, we provide the complete type inference rules
and show that our type inference algorithm is sound and complete.
The kinding and constraints rules are already shown in \cref{inference}.
The type inference rules are shown in \cref{rules:typing:full}.
The various theorems and their proofs are direct adaptations
of the equivalent statements for HM(X) \citep{sulzmann1997proofs}.

\clearpage
% \begin{figure}[tp]
%   \centering
%   \begin{mathpar}

%     % \inferrule{
%     %   \inferK{C \Cand C_x} \E \tau {k'} \\
%     %   D = C \Cand C_x \Cand \Cleq{k'}k
%     % }{
%     %   \E \vdash \Cleq{\forall \kvar_i \forall (\tvar_j:k_j).\ \qual{C_x}{\tau}}{k} \Crewrite  D
%     % }
%   \end{mathpar}
%   \caption{Auxiliary rules for inference}
%   \label{op:usgmap}
% \end{figure}

\input{infer/metatheory}

### 2019-07-10 kindly/infer/infer.tex
Add the proof for completeness.

\section{Inference}

An important innovation of \affe is its principal type inference.
We now formulate our inference algorithm
based on the $HM(X)$ framework~\citep{DBLP:journals/tapos/OderskySW99}.
$HM(X)$ presents a Hindley-Milner type system for a language
with qualified types where constraints are expressed in an arbitrary
constraint $X$. In particular, given some properties on the constraint system $X$,
$HM(X)$ ensures principal type inference.
We apply HM(X) to a concrete constraint language which we name $\CL$.
We adapt and extend its existing rules to support kind inference,
track linearity and handle borrows and regions. Finally, we
formulate an appropriate constraint solving algorithm for $\CL$.
In addition, our constraint solving algorithm simplifies constraints in a
principled way.
We first present various preliminary definitions
before showing our kind and type inference judgements
and our constraint solving algorithm.

@@

We note $\inferW{\Sv}{(C,\unif)}{\bf{\E}}{\bf{e}}{\tau}$ when
$e$\ has type $\tau$ in $\E$ under the constraints $C$ and unifier $\unif$
with a usage environment $\Sv$. $\E$ and $e$ are the input parameters of our
inference algorithm.
We revisit the syntax-directed rules presented in \cref{sdtyping} to highlight the
novelties
of our inference algorithm and the differences with the syntax-directed
system.

@@

\begin{theorem}[Completeness]
  Let $\inferS{C'}{\unif'\E}{e}{\schm'}$ a typing derivation,
  then $\inferW{\Sv}{(C,\unif)}{\Eflat\E}{e}{\tau}$
  for some substitution $\unif$, constraint $C$ and type $\tau$ such
  that
  \begin{align*}
    (C_\schm,\schm) &= \generalize{C}{\unif\E}{\tau}
    &\unif &\leq^{\phi}_{\fv{\E}} \unif'
    &\entail{C'&}{\phi C}
    &\entail{C'&}{\phi \schm \preceq \schm'}
    % &( C, \schm, \unif) &\leq (C',\schm',\unif')
  \end{align*}
\end{theorem}

>>>>

\section{Inference}
\label{inference}

An important contribution of \affe is its principal type inference.
We now formulate our inference algorithm
based on the $HM(X)$ framework~\citep{DBLP:journals/tapos/OderskySW99}.
$HM(X)$ is a Hindley-Milner type system for a language
with qualified types where constraints are expressed in an arbitrary
theory $X$.
Most important, given some properties on the constraint system $X$,
$HM(X)$ ensures principal type inference.
We apply HM(X) to a concrete constraint language which we name $\CL$.
We adapt and extend its existing rules to support kind inference,
track linearity and handle borrows and regions. Finally, we
formulate an appropriate constraint solving algorithm for $\CL$.
In addition, our constraint solving algorithm simplifies constraints in a
principled way.
We first present various preliminary definitions
before showing our kind and type inference judgements
and our constraint solving algorithm.

@@

We note $\inferW{\Sv}{(C,\unif)}{\bf{\E}}{\bf{e}}{\tau}$ when
$e$\ has type $\tau$ in $\E$ under the constraints $C$ and unifier $\unif$
with a usage environment $\Sv$. $\E$ and $e$ are the input parameters of our
inference algorithm.
We revisit the syntax-directed rules presented in \cref{sdtyping} to highlight the
novelties
of our inference algorithm and the differences with the syntax-directed
system.
As before, the complete type inference rules are shown in \cref{appendix:infer}.

@@

\begin{theorem}[Completeness]
  Let $\inferS{C'}{\unif'\E}{e}{\schm'}$ a typing derivation,
  then $\inferW{\Sv}{(C,\unif)}{\Eflat\E}{e}{\tau}$
  for some substitution $\unif$, constraint $C$ and type $\tau$ such
  that
  \begin{align*}
    (C_\schm,\schm) &= \generalize{C}{\unif\E}{\tau}
    &\unif &\leq^{\phi}_{\fv{\E}} \unif'
    &\entail{C'&}{\phi C_\schm}
    &\entail{C'&}{\phi \schm \preceq \schm'}
    % &( C, \schm, \unif) &\leq (C',\schm',\unif')
  \end{align*}
\end{theorem}
